---
title: "gwarfs"
author: "Sabrina Sandy"
date: "2024-03-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Rules of The Gerrymandering

If you're reading this before Gwarfs, sorry to ruin the magic but I did this to make it equitable and so that everyone would be happy and enjoy the Gwarfs. Here was my thought process for how this should go down.

1. Everyone should get at least one (1) award
2. If the award you won by vote is on the meaner side then you should by default get a second
3. There should be no outright sweeps
    - If there are, second most voted individual takes it
4. I am not eligible for any awards

### Let's get gerrymandering !

```{r, message= FALSE}
#import our libraries
library(tidyverse)
library(stringr)
library(fuzzyjoin)
library(janitor)


#import our data
gwarfs_df <- read_csv("data/Gwarfs Data Cleaned.csv")

# lets do some text cleaning too
gwarfs <- gwarfs_df %>%
  mutate_all(funs(tolower))
gwarfs

```

## Data Analysis 

Doing some data wrangling on the results of the survey (as of 27/03/24)

The Superlatives are as follows:
"Most Likely to Leave Sackville and Never Come Back"  
 [2] "Most Likely to Be Famous"                            
 [3] "Host(ess) with The Most(ess)"                        
 [4] "Most Likely to Be CEO by Our 5 Year Reunion"         
 [5] "Party Foul"                                          
 [6] "Most Likely to Be Late to The Function"              
 [7] "Best Off-Campus Memory"                              
 [8] "Best Harper Memory"                                  
 [9] "M.V.P"                                               
[10] "Always Allowed on AUX"                               
[11] "Most Likely to Have an Insane post Sackville Glow Up"
[12] "Funniest"                                            
[13] "Biggest Yum Yucker"                                  
[14] "Most Likely to End Up On The Most Wanted List"       
[15] "Academic Weapon 💥"                                  
[16] "Certified Yapper 🗣️"                                  
[17] "Peaked In College"                                   
[18] "Karaoke Legend(s) 🎤"                                
[19] "Peaked In High School"

```{r}


# let's drop the last two columns, we can make them into a data frame later
gwarfs <- gwarfs %>%
  select(1:19)
gwarfs

# I tried to do this multiple times, I'm doing this the long way 

# First let's get the ranks of all.....20 superlatives 

leave_sack_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Most Likely to Leave Sackville and Never Come Back"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE)%>%
  drop_na()
leave_sack_rank

famous_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Most Likely to Be Famous"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE)%>%
  drop_na()
famous_rank

host_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Host(ess) with The Most(ess)"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
host_rank

CEO_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Most Likely to Be CEO by Our 5 Year Reunion"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
CEO_rank

foul_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Party Foul"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
foul_rank

late_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Most Likely to Be Late to The Function"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
late_rank

offCampus_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Best Off-Campus Memory"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
offCampus_rank

harper_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Best Harper Memory"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
harper_rank

MVP_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("M.V.P"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
MVP_rank

AUX_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Always Allowed on AUX"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
AUX_rank

gloUp_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Most Likely to Have an Insane post Sackville Glow Up"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
gloUp_rank

funny_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Funniest"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
funny_rank

yumYuck_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Biggest Yum Yucker"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
yumYuck_rank

mostWanted_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Most Likely to End Up On The Most Wanted List"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
mostWanted_rank

weapon_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Academic Weapon 💥"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
weapon_rank

yapper_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Certified Yapper 🗣"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
yapper_rank

peakedCollege_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Peaked In College"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
peakedCollege_rank

karaoke_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Karaoke Legend(s) 🎤"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
karaoke_rank

HS_rank <- gwarfs %>%
  pivot_longer(
    cols = starts_with("Peaked In High School"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
HS_rank

# bind all these columns back together 

# sup_winners <- leave_sack_rank %>%
#   bind_cols(famous_rank)
# sup_winners






```


```{r}
# Now lets work on the people's choices

peoples_choice <- gwarfs_df %>%
  select(20:21)
peoples_choice

```

### Party Foul Wrangling

```{r}
# while the moment might be the same, people expressed them in different ways
# so we've gotta wrangle our data to count effectively

# let's subset only that column 
foul_df <- gwarfs %>%
  select("Party Foul")
foul_df

# then lets replace any istance of olivia with olivia kissing
foul_df$`Party Foul` <-
  ifelse(str_detect(foul_df$`Party Foul`, "olivia"), "olivia kissing", foul_df$`Party Foul`)

# then lets replace any istance of isaac with isaac yarf
foul_df$`Party Foul` <-
  ifelse(str_detect(foul_df$`Party Foul`, "isaac"), "isaac yarf", foul_df$`Party Foul`)

# then lets replace any istance of nora with nora puking on drew
foul_df$`Party Foul` <-
  ifelse(str_detect(foul_df$`Party Foul`, "nora"), "nora puking on drew", foul_df$`Party Foul`)

foul_df

foul_rank <- foul_df %>%
  pivot_longer(
    cols = starts_with("Party Foul"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
foul_rank
```


### Harper Memories Wrangling

```{r}
# let's subset only that column 
harper_df <- gwarfs %>%
  select("Best Harper Memory")
harper_df

# then lets replace any istance of olivia with olivia kissing
harper_df$`Best Harper Memory` <-
  ifelse(str_detect(harper_df$`Best Harper Memory`, "olivia"), "olivia's birthday/mario costume", harper_df$`Best Harper Memory`)

harper_df

harper_rank <- harper_df %>%
  pivot_longer(
    cols = starts_with("Best Harper Memory"),
    names_to = "superlative",
    values_to = "name") %>%
  count(superlative, name, sort = TRUE) %>%
  drop_na()
harper_rank
```



```{r}
# let's put these columns back together!
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Unused Code

```{r}
# # We want to see everyone's vote per superlative
# gwarfs_winner <- gwarfs %>%
#   # pivot longer so every superlative and the person nominated is an individual row
#   pivot_longer(1:19) %>%
#   rename(superlative =  name) %>%
#   # group by superlatives, goes 1-19 for each response
#   group_by(value, superlative) %>%
#   # count if there's a name value associated with the superlative
#   count() %>%
#   # pivot it wider so each superlative has an associated count for each name submitted
#   pivot_wider(id_cols = superlative, names_from = value, values_from = n, values_fill = 0)
# gwarfs_winner
# 
# # woohoo! we've got a good table going baby
# 
# # caelan's name was spelt tons of different ways, let's try to clean this up
# gwarfs_caelan_clean <- gwarfs_winner %>%
#   select(starts_with("ca")) %>%
#   mutate(caelan_sum = `caelan` + )
# gwarfs_caelan_clean
# 
# # seperate out the sum column of all those caelans
# gwarfs_caelan_remove <- gwarfs_caelan_clean %>%
#   select(caelan_sum)
# gwarfs_caelan_remove
# 
# # slap it back in there
# gwarfs_winner <- gwarfs_winner %>%
#   select(-c(8:11)) %>%
#   left_join(gwarfs_caelan_remove) %>%
#   rename(`caelan` = `caelan_sum`)
# gwarfs_winner
```

