---
title: "gwarfs"
author: "Sabrina Sandy"
date: "2024-03-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Rules of The Gerrymandering

If you're reading this before Gwarfs, sorry to ruin the magic but I did this to make it equitable and so that everyone would be happy and enjoy the Gwarfs. Here was my thought process for how this should go down.

1. Everyone should get at least one (1) award
2. If the award you won by vote is on the meaner side then you should by default get a second
3. There should be no outright sweeps
    - If there are, second most voted individual takes it
4. I am not eligible for any awards

### Let's get gerrymandering !

```{r }
#import our libraries
library(tidyverse)
library(stringr)


#import our data
gwarfs_df <- read_csv("data/Gwarfs Data Cleaned.csv")
gwarfs_df

# lets do some text cleaning too
gwarfs <- gwarfs_df %>%
  mutate_all(funs(tolower))
gwarfs
```

## Finding The Winners

Doing some data wrangling on the results of the survey (as of 27/03/24)

The Superlatives are as follows:
"Most Likely to Leave Sackville and Never Come Back"  
 [2] "Most Likely to Be Famous"                            
 [3] "Host(ess) with The Most(ess)"                        
 [4] "Most Likely to Be CEO by Our 5 Year Reunion"         
 [5] "Party Foul"                                          
 [6] "Most Likely to Be Late to The Function"              
 [7] "Best Off-Campus Memory"                              
 [8] "Best Harper Memory"                                  
 [9] "M.V.P"                                               
[10] "Always Allowed on AUX"                               
[11] "Most Likely to Have an Insane post Sackville Glow Up"
[12] "Funniest"                                            
[13] "Biggest Yum Yucker"                                  
[14] "Most Likely to End Up On The Most Wanted List"       
[15] "Academic Weapon 💥"                                  
[16] "Certified Yapper 🗣️"                                  
[17] "Peaked In College"                                   
[18] "Karaoke Legend(s) 🎤"                                
[19] "Peaked In High School"

```{r}


# let's drop the last two columns, we can make them into a data frame later
gwarfs <- gwarfs %>%
  select(1:19)
gwarfs


# We want to see everyone's vote per superlative
gwarfs_winner <- gwarfs %>%
  # pivot longer so every superlative and the person nominated is an individual row
  pivot_longer(1:19) %>%
  rename(superlative =  name) %>%
  # group by superlatives, goes 1-19 for each response
  group_by(value, superlative) %>%
  # count if there's a name value associated with the superlative
  count() %>%
  # pivot it wider so each superlative has an associated count for each name submitted
  pivot_wider(id_cols = superlative, names_from = value, values_from = n, values_fill = 0)
gwarfs_winner

# woohoo! we've got a good table going baby

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
